Comparing to lognormal, Poisson, exponential

### 2021-03-11 analysis/rev_prototyping/ct.Rmd
less memory

theme_set(theme_bw())
compare_props_off2 <- function(focal_sim, fs_df, ncomps = 100) {

  fs_df$sim_char = as.character(fs_df$sim)

  if(focal_sim != -99) {
    fs_df <- dplyr::filter(fs_df, sim > 0)
  }

  nsims <- unique(fs_df$sim_char)[ which(unique(fs_df$sim_char) != as.character(focal_sim))]

  if(length(nsims) == 0) {
    return(data.frame(focal_sim = focal_sim, mean_po_comparison = NA, n_po_comparisons = 0))
  }

  focal_sad <- dplyr::filter(fs_df, sim == focal_sim)

  compare_sims <- sample(nsims, size = min(length(nsims), ncomps), replace =F)

  compare_sads <- dplyr::filter(fs_df, sim_char %in% compare_sims)

  compare_props <- compare_sads %>%
    dplyr::group_by(sim) %>%
    dplyr::summarize(prop_off = proportion_off(t(data.frame(abund, focal_sad$abund)))) %>%
    dplyr::ungroup()

  return(compare_props)
}

@@

real_po <- proportion_off(t(data.frame(real_sad$abund, ct_sad$abund)))
sim_po <- compare_props_off2(ct_sad$sim[1], fs, ncomps = 3999)

>>>>

theme_set(theme_bw())

@@

real_po <- proportion_off(t(data.frame(real_sad$abund, ct_sad$abund)))
sim_po <- compare_props_off_full(ct_sad$sim[1], fs, ncomps = 3999)
